article title

### 2022-07-19 article.tex
Convert Greek text to table

\subsection{Greek mathematics}
\label{sec:greek_mathematics}

@@

\subsection{Greek text}
\label{sec:greek_text}

alpha \textalpha \textAlpha \\
beta \textbeta \textBeta \\
gamma \textgamma \textGamma \\
delta \textdelta \textDelta \\
epsilon \textepsilon \textEpsilon \\
zeta \textzeta \textZeta \\
eta \texteta \textEta \\
theta \texttheta \textTheta \\
iota \textiota \textIota \\
kappa \textkappa \textKappa \\
lambda \textlambda \textLambda \\
mu \textmu \textMu \\
nu \textnu \textNu \\
xi \textxi \textXi \\
omicron o O \\
pi \textpi \textPi \\
rho \textrho \textRho \\
sigma \textsigma \textSigma \\
tau \texttau \textTau \\
upsilon \textupsilon \textUpsilon \\
phi \textphi \textPhi \\
chi \textchi \textChi \\
psi \textpsi \textPsi \\
omega \textomega \textOmega \\

>>>>

\newpage
\subsection{Greek mathematics}
\label{sec:greek_mathematics}

@@

\newpage
\subsection{Greek text}
\label{sec:greek_text}

Greek letters can be inserted as text.

\begin{table}[H]
\begin{flushleft}
\begin{tabular}{lcccc}
\toprule
letter & code & miniscule & code & majuscule \\
\midrule
alpha    & \textbackslash textalpha   & \textalpha   & \textbackslash textAlpha   & \textAlpha \\
beta     & \textbackslash textbeta    & \textbeta    & \textbackslash textBeta    & \textBeta \\
gamma    & \textbackslash textgamma   & \textgamma   & \textbackslash textGamma   & \textGamma \\
delta    & \textbackslash textdelta   & \textdelta   & \textbackslash textDelta   & \textDelta \\
epsilon  & \textbackslash textepsilon & \textepsilon & \textbackslash textEpsilon & \textEpsilon \\
zeta     & \textbackslash textzeta    & \textzeta    & \textbackslash textZeta    & \textZeta \\
eta      & \textbackslash texteta     & \texteta     & \textbackslash textEta     & \textEta \\
theta    & \textbackslash texttheta   & \texttheta   & \textbackslash textTheta   & \textTheta \\
iota     & \textbackslash textiota    & \textiota    & \textbackslash textIota    & \textIota \\
kappa    & \textbackslash textkappa   & \textkappa   & \textbackslash textKappa   & \textKappa \\
lambda   & \textbackslash textlambda  & \textlambda  & \textbackslash textLambda  & \textLambda \\
mu       & \textbackslash textmu      & \textmu      & \textbackslash textMu      & \textMu \\
nu       & \textbackslash textnu      & \textnu      & \textbackslash textNu      & \textNu \\
xi       & \textbackslash textxi      & \textxi      & \textbackslash textXi      & \textXi \\
omicrdon & o                          & o            & O                          & O \\
pi       & \textbackslash textpi      & \textpi      & \textbackslash textPi      & \textPi \\
rho      & \textbackslash textrho     & \textrho     & \textbackslash textRho     & \textRho \\
sigma    & \textbackslash textsigma   & \textsigma   & \textbackslash textSigma   & \textSigma \\
tau    & \textbackslash texttau   & \texttau   & \textbackslash textTau   & \textTau \\
upsilon    & \textbackslash textupsilon   & \textupsilon   & \textbackslash textUpsilon   & \textUpsilon \\
phi    & \textbackslash textphi   & \textphi   & \textbackslash textPhi   & \textPhi \\
chi    & \textbackslash textchi   & \textchi   & \textbackslash textChi   & \textChi \\
psi    & \textbackslash textpsi   & \textpsi   & \textbackslash textPsi   & \textPsi \\
omega    & \textbackslash textomega   & \textomega   & \textbackslash textOmega   & \textOmega \\
\bottomrule
\end{tabular}
\label{tab:greek_text}
\caption{Greek text}
\end{flushleft}
\end{table}
